---
title: "Clean Energy Analysis"
output: html_notebook
---
# Setup
```{r}
library(tidyverse)
library(ggplot2)
```

Based on the LCV Website: https://scorecard.lcv.org/scorecard?year=2022 which presents us an overview of which kinds of environmental bills were voted on in the house, we can see which bills include similar topics (are similar enough to include in a Strattmann analysis)


# Clean Energy Bills in the House

## Import Data
```{r}
setwd("~/Desktop/HSG/Economics/BA_Thesis/code/data")
clean_energy_bills <- read.csv("scorecard-export.csv", header = TRUE, sep = ",")
view(clean_energy_bills)
```

Decide on which Clean Energy Areas to pursue:

1. Investment & Funding
```{r}

# create a new dataset out of clean_energy_bills where only the Rows are kept, if Vote.Name contains the words "Investment", "Funds", "Fund" or "Funding"
pattern <- "Investment|Investing|Funds|Fund|Funding"

investment_funding <- clean_energy_bills %>% filter(grepl(pattern, Vote.Name, ignore.case = TRUE))
view(investment_funding)

# create a new dataset out of investment_funding where only the Rows are kept, if Vote.Name doees not contain the words "Investment", "Funds", "Fund" or "Funding"
not_investment_funding <- clean_energy_bills %>% filter(!grepl(pattern, Vote.Name, ignore.case = TRUE))
view(not_investment_funding)


#filtering investment and funding, and then which of these bills also has the issues climate change and clean energy
pattern <- "Climate Change"
cl_en <- investment_funding %>% filter(grepl(pattern, Issues, ignore.case = TRUE))
view(cl_en)


```

2. Buidlings & Infrastructure
```{r}

pattern <- "Building|Schools|Buildings"
# create a new dataset out of clean_energy_bills where only the rows are kept, if Vote.Name contains the words stipulated in pattern
buildings <- clean_energy_bills %>% filter(grepl(pattern, Vote.Name, ignore.case = TRUE))
view(buildings)

# create a new dataset out of clean_energy_bills where only the rows are kept, if Vote.Name does not contain the words stipulated in pattern

not_buildings <- clean_energy_bills %>% filter(!grepl(pattern, Vote.Name, ignore.case = TRUE))
view(not_buildings)

```

3. Tax Credits

```{r}

pattern <- "Tax|Credits"
# create a new dataset out of clean_energy_bills where only the rows are kept, if Vote.Name contains the words stipulated in pattern
tax_credits <- clean_energy_bills %>% filter(grepl(pattern, Vote.Name, ignore.case = TRUE))
view(tax_credits)

# create a new dataset out of clean_energy_bills where only the rows are kept, if Vote.Name does not contain the words stipulated in pattern

not_tax_credits <- clean_energy_bills %>% filter(!grepl(pattern, Vote.Name, ignore.case = TRUE))
view(not_tax_credits)

```



4. Dirty Energy
```{r}
dirtyenergy <- read.csv("dirty_energy.csv")
view(dirtyenergy)


# pattern <- "Drilling"
# dirtyenergy2 <- dirtyenergy %>% filter(grepl(pattern, Issues, ignore.case = TRUE))
# view(dirtyenergy2)

pattern2 <- "Offshore"
dirtyenergy3 <- dirtyenergy %>% filter(grepl(pattern2, Vote.Name, ignore.case = TRUE))
view(dirtyenergy3)

pattern3 <- "Subsid"
dirtyenergy4 <- dirtyenergy %>% filter(grepl(pattern3, Vote.Name, ignore.case = TRUE))
view(dirtyenergy4)

```
