---
title: "Data Analysis of Roll Call Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

# Set Up

```{r, include=FALSE}
library(tidyverse)
library(ggplot2)
```


## Import Data

Importing the cleaned roll call data
```{r echo=FALSE}
df <- read_csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/cleaned_full_rollcall_votes.csv")
head(df)
```


## Simple Data Analytics (Financial Data)

```{r}
# amount contributed by fossil fuel firms

# group by Party

# group by District
```


## Mind changers 

determine which representatives changed their votes over the course of the three sessioncs (114,115 and 116th congress)

```{r mind changers, echo=FALSE}
# create a function that looks at each row and its Vote_count. If 3, then compares 3 observations (Vote.114, Vote.115 and Vote.116) -> do the values change? if yes, where? -> if 2 ->
```


