---
title: "Data Analysis of Roll Call Data"
output: html
---
The summary statistics and plots of the data can be found in the plots.qmd file in the same directory.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
# install.packages("pastecs")
library(pastecs)
```

```{r, include=FALSE}
source("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/src/analysis/data_analysis_files/data_prep_analysis.R")

df <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/cleaned/analysis_df.csv")
# view(df)

# df <- filter_session_data(df, "113")
# view(df)

```


### time and state fixed effects 
```{r}
## import df that determines years of env. significance?

```

### plot change in mind with each roll_call... (to be able to analyse the contribution better)
```{r}
# plot change in mind with each roll_call


```

### general OLS model
```{r}
ols <- lm(Vote_change_dummy ~ . - party, data = df)
summary(ols)
```

```{r}
ols_1 <- lm(Vote_change_dummy ~ party, data = df)
summary(ols_1)
```

regressing the vote change dummy on party affiliation, we find that the coefficient for the Republican party is 0.2, the intercept shows how likely a democrat is to change their voting behaviour, at 0.31, we can see that democrats are more likely to change their voting behaviour on methane related issues, with only the democrat variable at 0.05 being significant.
### subsample OLS 
here we only look at those who did change their voting behavior.
```{r mind changers, echo=FALSE}
# create a function that looks at each row and its Vote_count. If 3, then compares 3 observations (Vote.114, Vote.115 and Vote.116) -> do the values change? if yes, where? -> if 2 ->
```


