---
title: "Preliminary Results Presentation"
author: "Minna Heim"
format: 
    revealjs:
        slide-number: c/t #< collapsed/total
---

```{r setup, echo = FALSE, include = FALSE}
library(tidyverse)
library(ggplot2)
library(knitr)
library(plm)
source("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/src/analysis/analysis_prep_functions.R")

# read in data
df <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df.csv")
roll_call <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/cleaned/roll_call.csv")
contributions <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/cleaned/contributions.csv")
unique_id_reps <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/original/unique_id_reps.csv")
final_df <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/cleaned/final_df.csv")
df_subsample <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df_subsample.csv")
df_sum <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df_sum.csv")
df_fe <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df_fe.csv")
df_subsample_sum <- read.csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df_subsample_sum.csv")
```

# Data 

## Data Structure {.smaller}
::: {.panel-tabset}

### 1
* Roll Call Data 
    + 6 votes (2013,2016, 2017, 2018, 2019, 2021)
* Contribution Data 
    + Dirty - Oil, Gas, Coal, Mining
    + Clean - Alternative Energy, Environmental Industry
* Unique ID Data 
    + list of all house members & their member_id

\
\
Documentation available on my [Github Profile](https://github.com/minnaheim). 

### 2
#### Roll Call Dataset
```{r}
roll_call <- roll_call %>% relocate(name, .after = last_name)
kable(head(roll_call))
```

### 3
#### Contribution Dataset
Here my cleaned contribution data
```{r}
kable(head(contributions))
```

### 4
#### Unique IDs of all House Members
```{r}
kable(head(unique_id_reps))
```

### 5
#### Merged Dataset
```{r}
kable(head(final_df))
```

:::
## Data Cleaning {.smaller}

If I had to summarize 1 and a half months of work... 

\
merged each dataset with member_id using the fuzzyjoin package
```r
fuzzy_match <- function(x, y, max_dist = 2) {
    return(stringdist::stringdist(x, y) <= max_dist)
}

fuzzy_match_last <- function(x, y) {
    return(fuzzy_match(x, y, 1))
}
fuzzy_match_first <- function(x, y) {
    return(fuzzy_match(x, y, 2))
}

```
merged all datasets together 
```r
df <- fuzzy_left_join(
    roll_call,
    contributions,
    by = c("name", "party", "state", "member_id"),
    match_fun = list(`fuzzy_match_first`, `==`, `==`, `==`)
)
```

# Plots 
## Distribution of Contributions {.smaller}
```{r}
# Plot with limits applied on the x-axis
df_long <- df %>%
    pivot_longer(cols = starts_with("amount"), names_to = "contribution_type", values_to = "contribution_amount")

boxplot_1 <- ggplot(df_long, aes(x = contribution_amount, y = contribution_type)) +
    geom_boxplot()

boxplot_1
```

## Distribution of Vote Change by Party {.smaller}

```{r}

plot_4 <- df_long %>%
    group_by(party) %>%
    ggplot(aes(x = Vote_change_dummy, fill = party)) +
    geom_bar(position = "fill") +
    labs(x = "Vote Change", y = "Party") +
    scale_x_continuous(breaks = c(0, 1)) +
    scale_fill_manual(values = c("R" = "red", "D" = "blue"))

plot_4
```

Where D = 259 Representatives and R = 301 Representatives (if we only could those analysed, i.e. those who voted > 1 time)
<!-- D       259 -->
<!-- R       301 -->

<!--  D       326
 I         1
 R       402 -->

# Analysis

## Vote changes {.smaller}

Representatives who changed their votes = 23 
Total vote changes = 31

| Pro - Env | Anti - Env | Pro -> Anti | Anti -> Pro |
|:---------:|:-----:|:------:|:------:|
| 259      | 278  |    8 |   23   

# Models 
## General OLS {.smaller}

::: {.panel-tabset}
### original
```{r}
df_ols <- subset(df, select = -c(
    last_name, first_name, member_id, name, Vote_count, District,
    Vote3, Vote4, Vote51, Vote52, Vote6, Vote7, Vote_change, state
))

ols_1 <- lm(Vote_change_dummy ~ ., data = df_ols)
summary(ols_1)
```

### summarized
```{r}
df_sum <- subset(df_sum, select = -c(
    last_name, first_name, member_id, name, Vote_count, District,
    Vote3, Vote4, Vote51, Vote52, Vote6, Vote7, Vote_change, state
))

ols_sum <- lm(Vote_change_dummy ~ ., data = df_sum)
summary(ols_sum)
```

### sessionized
```{r}
df_114 <- filter_session_data(df, "114")
ols_114 <- lm(Vote_change_dummy ~ ., data = df_114)
summary(ols_114)
```

:::

## Subsample OLS {.smaller}

::: {.panel-tabset}

### Data
```{r}
kable(head(df_fe))
```


### OLS
Including only those representatives, where Vote_change_dummy == 1
```{r}
df_subsample <- subset(df_subsample, select = -c(
    last_name, first_name, member_id, name, Vote_count, District,
    Vote3, Vote4, Vote51, Vote52, Vote6, Vote7, Vote_change, state, Vote_change_dummy
))

ols_subsample <- lm(change ~ ., data = df_subsample)
summary(ols_subsample)
```

### sessionized
```{r}
df_subsample_sum <- subset(df_subsample_sum, select = -c(
    last_name, first_name, member_id, name, Vote_count, District,
    Vote3, Vote4, Vote51, Vote52, Vote6, Vote7, Vote_change, state, Vote_change_dummy
))

ols_subsample_sum <- lm(change ~ ., data = df_subsample_sum)
summary(ols_subsample_sum)
```

:::

## Subsample OLS incl. Fixed Effects

```{r}
df_fe <- df_fe %>% select(-c(
    last_name, first_name, name, District, Vote_count, Vote_change,
    first_contribution, Vote_change, Vote_change_dummy, member_id, Vote3, Vote4, Vote51, Vote52, Vote6, Vote7
))
# view(df_fe)

fixed <- plm(vote_change_type ~ ., data = df_fe, index = c("state", "year"), model = "within")
summary(fixed)
```

<!-- Integrating Entity and Time fixed effects (state and year), and control for party -->

## Problems 
* Integration of State Variable
    + doesnt produce coeff. in general OLS, probably won't in subsample either
* Negative Contribution Values
    + acc. to Open Secrets, due to refunds from previous campaign
* Fixed Effects Model
    + cannot run ols regressions with dataset (error: variables are factors of another, due to small n)
    + construct base contribution, as first contribution, or avg. of all before change
    + Should I calculate ∆contribution? 
* NA Problems 
    + still 83 out of 725 rows are NAs (Names too divergent)



## Future work

Things I still want to integrate into the data/models/thesis

* Improve FE dataset (?)
* Time of Contribution (analyse differences in 2 votes in the 115th congress)
* Remove remaining NAs in Data. 83 out of 725 rows are NAs.
* Robustness checks (with Logit/Probit)


```{r}
# install.packages("renderthis")
renderthis::to_pdf("quarto_render.html")
```
