---
title: "Plots for the paper"
format: html
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(e1071)
df <- read_csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df.csv", show_col_types = FALSE)
view(df)
df_long <- read_csv("/Users/minna/Desktop/HSG/Economics/BA_Thesis/code/data/analysis/df_long.csv", show_col_types = FALSE)
view(df_long)
```

With a function such as this one you can plot the contributions in dataset, i.e. for each election, how many contributions were made in line with the cutoff date, also plotted.

```{r}
# plot contributions and votes
df_long_1 <- df_long %>%
    filter(complete.cases(Vote)) %>%
    filter(complete.cases(Contribution_plus)) %>%
    filter(complete.cases(Contribution_minus)) %>%
    filter(Contribution_plus > 0) %>%
    filter(Contribution_minus > 0)
# pro environmental contributions
env_contribs <- ggplot(df_long_1, aes(as.factor(Vote), Contribution_plus)) +
    geom_boxplot() +
    scale_y_continuous(limits = c(0, 1000)) +
    labs(
        title = "Pro environmental contributions by pro-environmental vote",
        x = "Pro-environmental Vote",
        y = "Amount of contribution in 1000 USD"
    )
env_contribs

# anti environmental contributions
anti_env_contribs <- ggplot(df_long_1, aes(as.factor(Vote), Contribution_minus)) +
    geom_boxplot() +
    scale_y_continuous(limits = c(0, 1000)) +
    labs(
        title = "Anti environmental contributions by pro-environmental vote",
        x = "Pro-environmental Vote",
        y = "Amount of contribution in 1000 USD"
    )
anti_env_contribs

ggsave(path = "../../thesis/template-typst/figures", filename = "env_contribs.svg", plot = env_contribs, width = 6, height = 6, units = "in", dpi = 300)
ggsave(path = "../../thesis/template-typst/figures", filename = "anti_env_contribs.svg", plot = anti_env_contribs, width = 6, height = 6, units = "in", dpi = 300)

```

Notice how this is scaled the same way, the average contribution from anti_env is higher than the pro_env contributions. The reason behind this, is that many get 0, when removing 0, still looks like this.


```{r}
# distribution of pro environmental contributions and anti environmental contributions
# calculate mean of pro environmental contributions
# df_long <- df_long %>%
#     group_by(Instance) %>%
#     mutate(mean_plus = mean(Contribution_plus, na.rm = TRUE)) %>%
#     mutate(mean_minus = mean(Contribution_minus, na.rm = TRUE))

mean_plus <- df_long %>%
    summarise(mean_plus = mean(Contribution_plus, na.rm = TRUE)) %>%
    pull(mean_plus)
# [1] 9.906063
mean_minus <- df_long %>%
    summarise(mean_minus = mean(Contribution_minus, na.rm = TRUE)) %>%
    pull(mean_minus)
# [1] 197.9967

pro_plot_contribs <- df_long %>%
    ggplot(aes(x = Contribution_plus)) +
    geom_histogram(binwidth = 3) +
    labs(
        title = "Distribution of Pro Environmental Contributions",
        x = "Amount of Contributions in 1000 USD",
        y = "Frequency (log scale)"
    ) +
    geom_hline(yintercept = mean_minus, color = "red") +
    scale_y_continuous(trans = "log10")

# scale_y_continuous(limits = c(0, 350)) +
# scale_x_continuous(limits = c(0, 200))

pro_plot_contribs


anti_plot_contribs <- df_long %>%
    ggplot(aes(x = Contribution_minus)) +
    geom_histogram(binwidth = 3) +
    labs(
        title = "Distribution of Anti Environmental Contributions",
        x = "Amount of Contribution in 1000 USD",
        y = "Frequency (log scale)"
    ) +
    geom_hline(yintercept = mean_plus, color = "red") +
    scale_y_continuous(trans = "log10")
anti_plot_contribs



ggsave(path = "../../thesis/template-typst/figures", filename = "pro_plot_contribs.svg", plot = pro_plot_contribs, width = 6, height = 6, units = "in", dpi = 300)
ggsave(path = "../../thesis/template-typst/figures", filename = "anti_plot_contribs.svg", plot = anti_plot_contribs, width = 6, height = 6, units = "in", dpi = 300)
```


```{r}

# check skewness of contribution data to see whether we need to apply the log transformation

# pro environmental contributions
df_long <- df_long %>% filter(complete.cases(Contribution_plus))
skewness(df_long$Contribution_plus)

# anti environmental contributions
df_long <- df_long %>% filter(complete.cases(Contribution_minus))
skewness(df_long$Contribution_minus)
```

Interpretation: both very much skewed, so we need to apply log transformation to the contributions.
```{r}

df_long <- df_long %>%
    mutate(Contribution_plus_log = log(Contribution_plus + 1)) %>%
    mutate(Contribution_minus_log = log(Contribution_minus + 1))

skewness(df_long$Contribution_plus_log)

```


```{r}
# effect of party on contributions
party_contrib_pro <- df_long %>%
    ggplot(aes(x = party, y = Contribution_plus)) +
    geom_boxplot() +
    labs(
        title = "Pro environmental contributions by party",
        x = "Party",
        y = "Amount of contribution in 1000 USD"
    ) +
    scale_y_continuous(limits = c(0, 100))

party_contrib_pro

party_contribs_anti <- df_long %>%
    ggplot(aes(x = party, y = Contribution_minus)) +
    geom_boxplot() +
    labs(
        title = "Anti environmental contributions by party",
        x = "Party",
        y = "Amount of contribution in 1000 USD"
    ) +
    scale_y_continuous(limits = c(0, 100))

party_contribs_anti

# average pro environmental contributions by party
party_contribs_avg <- df_long %>%
    group_by(party) %>%
    summarise(mean_plus = mean(Contribution_plus, na.rm = TRUE)) %>%
    ggplot(aes(x = party, y = mean_plus)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Average pro environmental contributions by party",
        x = "Party",
        y = "Amount of contribution in 1000 USD"
    )

party_contribs_avg

# average anti environmental contributions by party
party_contribs_avg_anti <- df_long %>%
    group_by(party) %>%
    summarise(mean_minus = mean(Contribution_minus, na.rm = TRUE)) %>%
    ggplot(aes(x = party, y = mean_minus)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Average anti environmental contributions by party",
        x = "Party",
        y = "Amount of contribution in 1000 USD"
    )

party_contribs_avg_anti
```

```{r}
# ADD TO PLOTS FILE
# plot the distribution of the amount of E contributions by date
# indivs20_filtered_e <- indivs20 %>%
#     filter(str_detect(RealCode, "^E"))
# cutoff_date_1 <- "06-25-2020"

# plot_E_1y_prior <- indivs20_filtered_e %>%
#     ggplot(aes(x = Date, y = RealCode)) +
#     geom_point() +
#     geom_smooth() +
#     labs(
#         title = "Amount of E contributions by date - 1 year prior to vote is the line",
#         x = "Date",
#         y = "Amount"
#     ) +
#     geom_vline(xintercept = as.numeric(cutoff_date_1)) # Add a vertical line for the cutoff date

# plot_E_1y_prior


# cutoff_date_2 <- "12-25-2020"
# plot_E_6mo_prior <- indivs20_filtered_e %>%
#     ggplot(aes(x = Date, y = RealCode)) +
#     geom_point() +
#     geom_smooth() +
#     labs(
#         title = "Amount of E contributions by date - 16 months prior to vote is the line",
#         x = "Date",
#         y = "Amount"
#     ) +
#     geom_vline(xintercept = as.numeric(cutoff_date_2)) # Add a vertical line for the cutoff date

# plot_E_6mo_prior
```